Individual Variation in Animal Movement and Effects on Seed Dispersal Distance

### 2021-01-08 paper/paper.Rmd
knit to html
Tried to make figures in manuscript Rmd but word makes them horrible.

```{r setup, echo=FALSE}
knitr::opts_chunk$set(eval = FALSE, echo = FALSE)
```

@@

```{r eval = TRUE, fig.width=6}
set.seed(5)
library(ggplot2)
library(aracari)
library(cowplot)

>>>>

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

```{r libraries}
library(ggplot2)
library(aracari)
library(cowplot)
library(dplyr)

@@

```{r eval = TRUE, fig.width=6}
set.seed(5)
